Out-of-Sample Comparisons of Overfit Models

### 2017-04-21 2-setup.tex
[#40/move] Move extended example from Section 3.3 to appendix

\documentclass[12pt,draft]{article}
\input{setup}

\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
    would like to thank Julian Betts, Helle Bunzel,
    St\'ephane Bonhomme, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 NBER-NSF Time-Series
    Conference, and in many seminars at UCSD, and especially
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

\date{\VERSION}

\begin{document}
\maketitle

\begin{abstract}\noindent
  This paper uses dimension asymptotics to study the behavior of
  out-of-sample (OOS) test statistics when they are used to compare
  ``overfit'' linear regression models. Under these asymptotics, the
  number of predictors used by the larger model increases with the
  number of observations so that their ratio remains uniformly
  positive. This analysis gives a theoretical motivation for using
  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
  \textit{Econometrica}) allows a forecaster to conduct inference
  about the models' generalization error, an important measure of
  forecast accuracy that conditions on the models' parameter estimates.
  We show analytically and through Monte Carlo that standard full-sample
  test statistics can not test hypotheses about this measure of performance.
  Our paper also suggests that comparisons of overfit models require small
  OOS test samples. If $P$ denotes the number of observations used for the
  OOS comparison and $T$ the total number of observations, $P^2/T$ must
  converge to zero for the OOS $t$-test to be centered on the model's
  generalization error.

\noindent JEL Classification: C12, C22, C52, C53

\noindent Keywords: Generalization Error, Forecasting, Model
Selection, $t$-test, Dimension Asymptotics
\end{abstract}
\newpage

\section{Introduction}
\label{sec:introduction}

Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use out-of-sample (OOS) instead of in-sample
comparisons: the DMW OOS test\footnote{%
  In this paper, we will refer to the basic OOS $t$-test studied by
  \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo simulations
that standard full-sample test statistics can not test hypotheses
about this performance.

Our paper also shows that popular test and training sample sizes may
give misleading results if researchers are concerned about overfit.
We show that $P^2/T$ must converge to zero for the DMW test to give
valid inference about the expected forecast accuracy, otherwise the
test measures the accuracy of the estimates constructed using only the
training sample.  In empirical research, $P$ is typically much larger
than this.  Our simulations indicate that using large values of $P$
with the DMW test gives undersized tests with low power, so this
practice may favor simple benchmark models too much.  Existing
corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
too often when the benchmark model is more accurate.

Although OOS comparisons have been popular in Macroeconomics and
Finance since \citepos{MeR:83} seminal study of exchange rate models,
it has been unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using OOS comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the $F$-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular OOS test statistics under conditions
that would justify these full-sample tests.  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons \citep[see][for a
review of this literature]{Wes:06}.\footnote{%
  Like us, \citet{Ana:07} allows the number of regressors to increase
  with $T$.  But in that paper, the number of regressors increases
  slowly enough that the OLS coefficients are consistent and
  asymptotically normal.} %
\citet{GiW:06} and
\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
derive an OOS test for the null hypothesis that the difference
between two models' OOS forecasting performance is unpredictable, a
martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
forecasting performance of a model suffers from a breakdown relative
to its in-sample performance; and \citet{GiR:10} test whether the
forecasting performance is stable. However, those papers focus on a
particular OOS estimation strategy and do not address why OOS
comparisons might be useful as a general strategy.

Since in-sample and OOS statistics require similar assumptions and
test similar hypotheses, one might expect that they would give similar
results.  They do not.  In-sample analyses tend to support more
complicated theoretical models and OOS analyses support simple
benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
\citet{GoW:08}.  Since these different approaches strongly influence
the outcome of research, it is important to know when each is
appropriate.  The explanations in favor of OOS comparisons claim
that they should be more robust to unmodeled instability
\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
comparison is invalid and the OOS comparisons are more reliable.  Of
course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
methods could be valid, but the OOS methods could have lower power.

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of OOS comparisons when at least
one of the models is overfit---the number of its regressors
increases with the number of observations so that their ratio remains
positive.  Although overfit is sometimes used to describe the
situation where a forecaster chooses from many different models,
i.e. \emph{data-mining} or \emph{data-snooping}, we view these as
separate issues.  Procedures that account for the presence of many
models have been, and are continuing to be, developed \citep[see, for
example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
whether those procedures should themselves use in-sample or OOS
comparisons.  Understanding the difference between in-sample and OOS
comparisons in the context of a simple comparison between two models
is necessary before resolving any new issues that arise with multiple
comparisons. Moreover, the empirical research that motivates
this paper uses \emph{pseudo} OOS comparisons and not
true OOS comparisons.  Even if a true OOS comparison
could account for some forms of data-snooping better than
\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
OOS comparisons would both be affected by the data-snooping, a
point also made by \citet{InK:04}.

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic conclusions should be true for other
models and estimation strategies as well.  Under this
asymptotic theory, where the number of regressors $K$ increases with $T$
so that the limit of $K/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the data available in period
$T$.\footnote{%
  See, for example, \citet{HTF:08} for a discussion of generalization
  error.} %
Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudotrue
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{%
  In a pair of papers similar to ours, \citet{ClM:12,ClM:12b} study
  in-sample and OOS tests that the larger model has nonzero
  coefficients that are too close to zero to expect the model to
  forecast more accurately.  Like this paper, they argue that the
  larger model can be true but less accurate.  However, they focus on
  an aspect of the DGP that makes this phenomenon likely, while we
  focus on the coefficient estimates that produce less accurate
  forecasts.  Moreover, the implications of our asymptotic theories
  are different and their papers do not provide reasons to do OOS
  comparisons.} %
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99}, and
\citealp{StW:03}, among others), but we show that this breakdown
can be caused by overfit as well.

It is important to realize that we are not \emph{advocating} linear
regression for highly overparametrized models. If $K$ is very large
relative to $T$, researchers will often want to use some form of
shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
model \citep{StW:02,BaN:02}. Our main focus is practical settings
where $K$ is \emph{moderately} large and it is not clear whether
overfit will dominate the results. In these settings it is
crucial to understand the behavior of different evaluation criteria
when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
methods for estimating these overfit models' performance. This is the goal of
this paper.

Our theoretical results partially justify OOS comparisons when
researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in this setting, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.  We show that the DMW test
lets the forecaster control the probability of the first error, just
as with conventional hypothesis testing.

But we also identify new practical limitations for applying the DMW
test to overfit models.
Since the models' coefficients are imprecisely estimated in the limit,
the test sample must be small enough that the model estimated over the
training sample is similar to the one that will be estimated over the
full sample.  In particular, $P/T \to 0$ is required for consistent
estimation of the difference in the two models' performance,
and $P^2/T \to 0$ is required for valid confidence
intervals and inference.  For larger $P$, the OOS comparisons remain
asymptotically normal, but are centered on the forecasting performance
associated with the period $R$ estimates.  In practice, researchers
typically use large values of $P$, so these studies may be too
pessimistic about their models' future accuracy if they use the DMW
test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
the DMW test under this limit theory.

Popular in-sample tests and model selection criteria, like the Wald
test and the AIC, do not help forecasters in this setting. We show
that these statistics do not select the more accurate model when
choosing between overfit models. For many DGPs the Wald test
will choose the larger model over a small benchmark
with probability much greater than its nominal size, regardless of
which model is more accurate, and the AIC behaves similarly. The BIC,
however, chooses the benchmark model with probability approaching one
even when the \emph{alternative} model is more accurate.\footnote{%
  Our result holds for a broad class of full-sample statistics, but
  there may be other potential statistics that mimic the OOS test and
  remain valid. Exploring such statistics is left for future
  research.} %
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.\footnote{%
  Also see \citet{Efr:86,Efr:04} for a discussion of naive in-sample
  loss comparisons.} %
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.\footnote{%
  Our theoretical results apply directly to \citepos{Mcc:07} OOS
  $t$-test, since it simply proposes more liberal critical values for
  the same test statistic that we study.  Since \citet{ClW:06,ClW:07}
  use a finite length estimation window, our asymptotics are
  incompatible with theirs and prevent us from studying their test
  directly, as well as \citepos{GiW:06} and other tests based on
  \citepos{GiW:06} asymptotics.  But \clws\ test can be viewed as a
  stochastic adjustment to the critical values of the usual \oost\
  test, so our conclusions should apply informally as well.
  Specifically, we show that the DMW test rejects with probability
  equal to nominal size when the estimated benchmark model is expected
  to be more accurate, so more liberal critical values result in
  overrejection.} %
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is misspecified but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

Finally, this paper introduces a new method of proof for OOS
statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
that sequences of OOS loss behave like mixingales when the
underlying series are absolutely regular, even if the forecasts depend
on non-convergent estimators.  Moreover, we also show that transformations of these
processes behave like mixingales after they are appropriately recentered, so
many arguments used to prove asymptotic
results for Near Epoch Dependent (NED) functions of mixing processes
can be used for these OOS processes with only slight modification.

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
DMW OOS test, shows that standard in-sample tests reject the
benchmark model too often when it is misspecified but more accurate than the
alternative, and shows that standard model selection methods can run
into similar problems. Section~\ref{sec:theory} also presents an
example DGP that illustrates these results. Section~\ref{sec:mc}
presents a Monte Carlo study supporting our theoretical results.
Section~\ref{sec:empirics} applies the OOS statistic to
\citepos{GoW:08} dataset for equity premium prediction, and
Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
are listed in the Appendix.

@@

These assumptions are broadly similar to those existing in the
literature, with some differences in our assumptions relating the
estimated coefficients to future values of the DGP.
Section~\ref{sec:example} contains an extended example that shows how
these assumptions are satisfied in a simple setting.

\section{Theoretical results}
\label{sec:theory}

This section lays out our theoretical results. The first subsection
presents results for the DMW \oost\ test; we show that it is
asymptotically normal when one or both forecasting models is overfit.
(i.e., under our increasing-$K$ asymptotic approximation.) We also
present a new limitation on these statistics---OOS comparisons heavily
penalize overfit models unless the size of the test sample is a very
small proportion of the total sample size, which will not be practical
in much applied research. The second subsection presents results for
full-sample statistics and shows that widely used test statistics and
model selection criteria are misleading when choosing a model for
forecasting. In contrast to OOS comparisons, these full-sample
criteria choose overfit models too often, even when they are less
accurate than simple benchmark models. These results are somewhat
abstract, so the third subsection works through an example DGP in
detail.

\subsection{Asymptotic normality of the DMW test}
\label{sec:oostheory}

This section has two main conceptual results. The first,
Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
asymptotically normal as the size of the test sample grows, even when
the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
difference in the generalization error of the models estimated over
the \emph{training sample}, which is not the quantity of interest to
forecasters. Forecasters will generally want to estimate or test
hypotheses about the difference in the generalization error of the
models estimated with the full sample, $\E_T \oosB$. Our second
result, Lemma~\ref{res-convergence}, shows that these quantities are
approximately equal only when the test sample is very small relative
to the total sample size. In particular, we show that $\oosA$ is a
consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
establishing these Lemmas, we then show that the \oost\ test is
asymptotically standard normal and can be used to test hypotheses
about $\E_T \oosB$, which requires the two Lemmas as well as a
consistent estimator of the variance of the OOS average.

In the first result, we show that
$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
\infty$. This application of the CLT is complicated by a hidden source
of dependence---the training sample estimators $\bh{iR}$. Under
conventional asymptotic theory, we would replace each $\bh{iR}$ with
its pseudotrue value $\theta_i$ and apply the CLT to
$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
arising from the replacement (as in \citealp{Wes:96},
\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
make that replacement here, because our asymptotic approximation
prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.

Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
satisfies the CLT. Mixingales satisfy a weak-dependence condition
similar to MDSes,\footnote{%
  An array $Z_{n,t}$ and an increasing sequence of \sfields
  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
  an array of constants $\{c_{n,t}\}$ and a sequence of constants
  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
  \begin{equation*}
    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
    \leq c_{n,t} \zeta_l
    \qquad\text{and}\qquad
    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
    \leq c_{n,t} \zeta_{l+1}.
  \end{equation*}
  Mixingales were introduced and developed by
  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
but they have some limitations. Transformations of mixingales are
typically not themselves mixingales, which means that CLTs for
mixingale processes require additional assumptions to hold beyond the
mixingale property.\footnote{%
  See \citet{Jon:97} for an illustration. We will borrow heavily from
  his results in our proofs.} %
This is in contrast to Near Epoch Dependent (NED) processes, which
retain the NED property after transformations. \citep[See chapter 17
of][for further discussion of these properties.]{Dav:94} But the OOS
loss has more structure than most mixingales and behaves like an NED
process in important respects. (The key result here is
Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
CLT that we use later, and Section~\ref{sec:example} works through an
i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
MDS and is easier to work with.

\begin{lem}\label{res-mixingale}
  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
  Moreover
  \begin{equation}
    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
  \end{equation}
  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
\end{lem}

It may be helpful to compare Lemma~\ref{res-mixingale} to the method
of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
is asymptotically normal when the forecasts are estimated with a fixed
length rolling window. In that case, each $\bh{it}$ depends on only
the most recent $R$ observations and, since $R$ is fixed in their
theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
mixing processes. Transformations of their forecast errors are
still obviously mixing processes and obey the CLT.

In our paper, $R$ is not fixed and the forecast errors are not a
convenient weakly-dependent process, since the estimation error in
$\bh{it}$ introduces strong dependence. Consequently,
transformations of the forecast errors are not weakly dependent
either. But this additional dependence has a special form and can be
removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.

The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
the models' generalization error. Under conventional asymptotics,
these quantities are generally close. But they are not for overfit
models and the models will tend to forecast better when estimated over the
full sample than over the training sample. Consequently, OOS
comparisons will penalize overfit models too much unless the test
sample is small relative to the total data set.

\begin{lem} \label{res-convergence}
  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
  \begin{equation}\label{eq:7}
    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
    + o_p(Q^{-1/2}).
  \end{equation}
\end{lem}
We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
approximating the performance of the full-sample estimates with that
of the partial-sample estimates. The key term on the RHS
of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
small, this noise dominates the OOS average, making it an inconsistent
estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
unrestrictive in our applications because we will multiply the OOS
average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
term has some implications for interpreting these results: we can only
measure the average performance of the forecasting models for an
extended period in the future, long enough that the future
observations are essentially independent of the current
information. For $Q=1$, for example, the dependence between
$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
strong.

Finally, we can use Lemmas~\ref{res-mixingale}
and~\ref{res-convergence} to show that the DMW test is asymptotically
normal and centered at $\E_T \oosB$, as long as
Assumption~\ref{asmp-4}b holds.

\begin{thm}\label{res-oost}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
  of $\oosA$,
  \begin{equation}
    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
    \vWeight.
  \end{equation}
  Then
  \begin{equation}
    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
  \end{equation}
\end{thm}

The requirement that $\sigma^2$ be uniformly a.s. positive is not
restrictive under our asymptotic theory. Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the DGP.  This
is intuitively similar to \citepos{GiW:06} rolling-window result, but
comes from different asymptotic theory; Giacomini and White keep the
variance of the OOS average positive by letting $P \to \infty$ with
$R$ fixed; in this paper, $R \to \infty$ but the variance remains
positive since $K \to \infty$ (quickly) as well.

If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
asymptotic theories would apply and the \oost\ test would remain normal as long
as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
approximation, the variance will converge to zero whenever the true
DGP is nested in both of the forecasting models. The same principles
may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
0$. It is likely that a second order expansion along the lines of
\citet{Mcc:07} would lead to asymptotic normality for that
intermediate case, but we leave that issue to future research.

Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
use to construct confidence intervals for $\E_T \oosB$ and test
hypotheses about $\E_T \oosB$. In particular, forecasters will often
want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
that the benchmark model is expected to be more accurate than the
alternative model in the future.

\begin{thm}\label{res:oostest}
  Suppose that the conditions of Theorem
  \ref{res-oost} hold. Then each of the usual Gaussian
  confidence intervals,
  \begin{gather}
    [\oosA - z_{\alpha/2} \, \sh /
    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
    \intertext{and}
    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
  \end{gather}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
  positive then
  \begin{equation}\label{eq:23}
    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
    \oosB \leq 0] \leq \alpha.
  \end{equation}
\end{thm}
\noindent
The results for confidence intervals in Theorem~\ref{res:oostest}
follow immediately from Theorem~\ref{res-oost},
but~\eqref{eq:23} requires additional proof.

\subsection{Failure of in-sample statistics for forecast evaluation}
\label{sec:insample}

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.\footnote{%
  \citet{Ana:12} shows that the Wald test is invalid in general and
  gives an adjustment that corrects the critical values; he also shows
  that the $F$-test is asymptotically valid under certain conditions
  on the distribution of the regressors.  \citet{Cal:11c} shows that
  the $F$-test is asymptotically invalid without Anatolyev's
  constraint, even under homoskedasticity, and provides a correction
  that gives valid tests.  Both papers only consider independent
  observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.\footnote{%
  In this section, we define
  $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$ and
  $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last
  $K_2 - K_1$ elements of $\theta_2$, and assume that the regressors
  are ordered so that the first $K_1$ elements of $x_{2,t}$ correspond
  to $x_{1,t}$.} %

The full-sample statistics we study in this paper share a common
property. They choose the alternative model when the distance between
a subset of their coefficient estimates and the origin exceeds a
threshold, and choose the benchmark otherwise. For the Wald test, for
example, this threshold is chosen so that the test has correct size
when those coefficients are zero in population. For small models that
can be consistently estimated, these coefficient estimates are close
to their true values and so this criterion can be a reasonable proxy
for the relative accuracy of the larger model.

But for overfit models, the estimates will typically be far from both
their pseudotrue values and also from zero. In that case, the Wald test and
the AIC will both tend to choose the larger model even when it is less
accurate than the smaller benchmark model. This phenomenon is driven
by the dimensionality of the alternative model, since there are more
potential values of the coefficient estimator that are far from zero
when it has many elements. The threshold for the Wald test and the AIC
is set by construction to be a bounded distance from the origin, and
every other statistic that shares this property has the same behavior
and can reject the benchmark model with high probability, even when
it is more accurate. This behavior is
formalized in Theorem~\ref{res:insample1}.

\begin{thm}\label{res:insample1}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
  $\Lambda$ be a model selection statistic that takes the values zero
  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
  $L(e) = e^2$ and that there exist a deterministic scalar $c$
  and a sequence of possibly random matrices $V_T$ such that
  \begin{equation}\label{eq:25}
    \limsup_{T \to \infty}
    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
    \to 0
  \end{equation}
  where the eigenvalues of $V_T$ are uniformly bounded in probability,
  $\plim \rank(V_T)/T > 0$, and neither $V_T$ nor $c$ depend on
  $\theta$ or the value of $\bh{2T}$.

  Then there exist DGPs satisfying these assumptions such that
  \begin{equation}\label{eq:11}
    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
  \end{equation}
\end{thm}

As we state above,~\eqref{eq:11} means that, with high probability,
the benchmark model is rejected even when it is more accurate. In
general, $\delta$ can be made arbitrarily small by increasing the
region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
chosen to put the limiting quantity in~\eqref{eq:11}
arbitrarily close to 1 while still satisfying
the assumptions of the Theorem.  The DGPs and
statistics used in Theorem~\ref{res:insample1} are simple and
common. They include correctly specified linear models with normal and
homoskedastic errors; and the statistics that meet the restrictions on
$\Lambda$ include the $F$-test and AIC.

For example, the $F$-statistic for the null hypothesis that the
benchmark model is correctly specified is known to have the form
\begin{equation*}
  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
    \bh{2T}}{s^2 (K_2 - K_1)}
\end{equation*}
where $s^2$ is the usual estimator of the variance of the regression
error. Then let $c$ be any number greater than 1 and define
\begin{equation*}
  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
  M_2' \big)^{-1} M_2'.
\end{equation*}
If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
satisfies~\eqref{eq:25}.
Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
for similar reasons, and the AIC for nested linear models is
equivalent to using the $F$-test with the critical value %
$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
as well.

For statistics that don't satisfy~\eqref{eq:25}, the behavior can be
quite different. The BIC, for example, can also be written in terms of
the $F$-statistic and is equivalent to using the critical value $(T \,
e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$. This
critical value diverges as $T \to \infty$, ensuring that~\eqref{eq:25}
fails for any $c$. For this statistic, we have the opposite problem as
before: when the alternative model is \emph{more} accurate, the
coefficient estimates of the larger model are contained in a bounded
region of the parameter space. Since the acceptance region of the BIC
grows, it eventually contains \emph{any} bounded region of the
parameter space. For large enough $T$, the BIC will always choose the
\emph{smaller model}, even when the larger model is more accurate.

This behavior is formalized in Theorem~\ref{res:insample2}.
\begin{thm}\label{res:insample2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
  e^2$, and let $\Lambda$ be a model selection statistic as in
  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
  $c$,
  \begin{equation}\label{eq:27}
    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
    \quad \text{as } T \to \infty.
  \end{equation}

  Then there exist DGPs satisfying these assumptions such that
  \begin{equation}\label{eq:15}
    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
  \end{equation}
\end{thm}

The condition~\eqref{eq:27} requires that the acceptance region of
$\Lambda$ eventually contains any finite cylinder centered at the
origin. Again,~\eqref{eq:15} implies that statistics like the BIC
will always choose the smaller model for some DGPs, even when the
larger model will give more accurate forecasts. Both models may be
overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.

It is important to remember that previous research, such as
\citet{Cal:11c} and \citet{Ana:12}, does not predict these
results. When $\Lambda$ represents a test statistic, the test may have
correct size for the null hypothesis that the additional coefficients
on the larger model are zero. The results in this subsection are being
driven by the full-sample statistics' behavior when the smaller model
is misspecified but more accurate.

Any statistic that uses the distance of the models' estimated
coefficients from a set point (the origin being the most common) is
poorly suited for choosing between overfit forecasting models. These
models only forecast well when their coefficient estimates are close
to their pseudotrue values, which can be far from the origin or any
other prespecified
point. Depending on the statistic, it can be biased towards choosing
the larger model or the smaller model. Formal in-sample \emph{tests}
will likely be biased towards the larger model, as we show for the
$F$-test and Wald test in Theorem~\ref{res:insample1}.

\subsection{An extended simple example}
\label{sec:example}

>>>>

@@

These assumptions are broadly similar to those existing in the
literature, with some differences in our assumptions relating the
estimated coefficients to future values of the DGP.
